R dyntrace report

### 2018-04-03 graphs/report-basic-info.Rmd
Report basic info.

#aggregated_functions %>% filter(!is.na(ERR1) || !is.na(ERR2)) %>% print

@@

aggregate_basic_info <- 
  basic_info %>% summarise(
    name="*",
    datasets=paste(name, collapse=", "),
    n.datasets=n(),
    n.functions=(aggregated_functions %>% count %>% pull(n)),
    n.calls=sum(n.calls),
    n.promises=sum(n.promises),
    n.promise.forces=sum(n.promise.forces),
    n.promise.lookups=sum(n.promise.lookups), 
    n.alien.promises=sum(n.alien.promises),
    n.alien.promise.forces=sum(n.alien.promise.forces)
  )

@@

 # some graphical stuff
 package_figure_width <- 10
 package_figure_columns <- min(7, ceiling(sqrt(n.packages)))
 package_figure_rows <- ceiling(n.packages/package_figure_columns)
 package_figure_height <- ceiling(10/7 * package_figure_rows)
```

# Dataset

>>>>

# FIXME aggregated_functions %>% filter(!is.na(ERR1) || !is.na(ERR2)) %>% print

@@

 aggregate_basic_info <- 
   basic_info %>% summarise(
     name="*",
     datasets=paste(name, collapse=", "),
     n.datasets=n(),
     n.functions=NA # FIXME (aggregated_functions %>% count %>% pull(n)),
     n.calls=sum(n.calls),
     n.promises=sum(n.promises),
     n.promise.forces=sum(n.promise.forces),
     n.promise.lookups=sum(n.promise.lookups), 
     n.alien.promises=sum(n.alien.promises),
     n.alien.promise.forces=sum(n.alien.promise.forces)
   )

@@

 # some graphical stuff
 package_figure_width <- 10
 package_figure_columns <- min(7, ceiling(sqrt(n.packages)))
 package_figure_rows <- ceiling(n.packages/package_figure_columns)
 package_figure_height <- ceiling(10/7 * package_figure_rows)
```
# Dataset
